WIDS 2024 Final Project

### 2024-01-11 Code/R FIle.qmd
fixed graph labels

```{r}
full_ntl_data |> 
  filter(year >= 1984) |> 
  ggplot(aes(x = year)) +
  geom_line(aes(y = mean_income), color = "red") +
  geom_line(aes(y = median_income), color = "blue") +
  theme_minimal() +
  labs(
    title = "Mean and Median Income in the United States Between 1984 and 2019",
    subtitle = "Using mean (red) and median (blue) incomes adjusted to 2020 rates",
    x = "Year",
    y = "Income in USD (Adjusted for Inflation to 2020 Rates)"
  )
```

>>>>

```{r}
full_ntl_data |> 
  filter(year >= 1984) |> 
  ggplot(aes(x = year)) +
  geom_line(aes(y = mean_income), color = "red") +
  geom_line(aes(y = median_income), color = "blue") +
  theme_minimal() +
  labs(
    title = "Mean and Median Income in the United States Between 1984 and 2019",
    subtitle = "Using mean (red) and median (blue) incomes",
    x = "Year",
    y = "Income in USD"
  )
```
